Social Computing Article\thanks{This title is temporary}

### 2013-01-10 Article.tex
commit

%%%% ijcai11.tex

\typeout{IJCAI-13 Instructions for Authors}

% These are the instructions for authors for IJCAI-13.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai13.sty is the style file for IJCAI-13 (same as ijcai07.sty).
\usepackage{ijcai13}

% Use the postscript times font!
\usepackage{times}

\usepackage{latexsym}

\title{Social Computing Article\thanks{This title is temporary}}
\author{Tabajara, Lucas \\
Institute of Informatics \\
Federal University of Rio Grande do Sul\\
Brazil \\
lmtabajara@inf.ufrgs.br
\and
Prates, Marcelo \\
Institute of Informatics \\
Federal University of Rio Grande do Sul\\
Brazil \\
morprates@inf.ufrgs.br}

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface. As a result, each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $X(k)$.

@@

This rule is similar to the {\em naked singles} rule. It is able to mark cells with more than one candidate value by looking for cells that are the only cells in their row, column or $3 \times 3$ block that can hold a particular value.

@@

This rule applies to groups of three contiguous $3 \times 3$ blocks. It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third. It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks. If the resulting set has cardinality $1$, the rule has successfully found one cell to mark.

@@

@@

>>>>

%\documentclass{article}
%\usepackage{ijcai13}
%\usepackage{times}
%\usepackage{latexsym}

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing

\usepackage{graphicx}

\title{Social Computing Article\thanks{This title is temporary}}

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface. As a result, each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.

@@

This rule is similar to the {\em naked singles} rule. It is able to mark cells with more than one candidate value by looking for cells that are the only ones in their row, column or $3 \times 3$ block that can hold a particular value.

@@

This rule applies to groups of three contiguous $3 \times 3$ blocks. It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third. It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks. If the resulting set has cardinality $1$, the rule has successfully found a cell to mark.

@@

\subsection{Copying Solutions}

In a study conducted by~\cite{farenzena:collabem}, subjects were invited to solve {\em Sudoku} puzzles and share them with other subjects with whom they were connected through a network topology. At any time, a player could copy solutions from one of his or her neighbours. The authors' analysis has shown that there is a different copy frequency associated with each topology. For instance, the scale free topology with $\gamma = 1.65$ resulted in a copy frequency of $87 \%$, while the fully connected topology resulted in a copy frequency of $42 \%$.

We incorporated this copying frequency into our modelling, recreating the scenario of the experiments conducted by~\cite{farenzena:collabem} by setting this parameter accordingly to the topologies we used.

\subsection{Conformist Behaviour}

We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents tend to copy a particular solution with probability $1$ when surrounded by neighbours that share this solution.

Our approach was to establish a {\em treshold} determining a minimum necessary quantity $N$ of neighbours sharing a particular solution. In our modelling, all agents with $N$ or more neighbours having a solution $s$ in common are programmed to copy solution $s$ from them.

\subsection{Guessing and Backtracking}

We have consistent evidence that trial-and-error is a part of the {\em Sudoku} solving experience. The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}. Some puzzles are only solvable by the means of a backtracking procedure (see Figure 1).

\begin{figure}
\centering
\includegraphics[scale=0.30]{trial_and_error_sudoku}
\caption{A {\em Sudoku} puzzle solvable only by trial-and-error}
\label{fig:trial_and_error_sudoku}
\end{figure}

In our modelling, we associate each agent with a numerical parameter determining the probability of this agent to guess when incapable of applying a typical {\em Sudoku} solving strategy.

Automatic {\em Sudoku} solvers employing a backtracking algorithm are easily programmed and very time-efficient. On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy. With this in mind, we propose in our modelling two different kinds of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}.

\begin{itemize}

\item
Local Backtracking: When faced with one or more conflicts in its own solution, an agent simply erases the conflicting cells.
\item
Social Backtracking: When faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours. In our modelling, this is done by raising the copy rate of this particular agent to $1$.

\end{itemize}

@@

\section{Acknowledgements}

Research partly supported by CPNPq and CAPES, Brazil.
